Imputation of Incomplete Multilevel Data with \proglang{R}

### 2023-11-22 Manuscript/Imputation_of_Incomplete_Multilevel_Data.tex
render

\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{ulem}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

Many datasets include individuals that are clustered together, for
example in geographic regions, or even different studies. In the
simplest case, individuals (e.g., students) are nested within a single
cluster (e.g., school classes). More complex clustered structures may
occur when there are multiple hierarchical levels (e.g., students in
different schools or patients within hospitals within regions across
countries), or when the clustering is non-nested (e.g., electronic
health record data from diverse settings and populations within large
databases). With clustered data we generally assume that individuals
from the same cluster tend to be more similar than individuals from
other clusters. In statistical terms, this implies that observations
from the same cluster are not independent and may in fact be correlated.
If this correlation is left unaddressed, estimates of \emph{p} values,
confidence intervals even model parameters are prone to bias
\citep{loca01}. Statistical methods for clustered data typically adopt
hierarchical models that explicitly describe the grouping of
observations. These models are also known as `multilevel models',
`hierarchical models', `mixed effect models', `random effect models',
and in the context of time-to-event data as `frailty models'. Table
\ref{tab:clus} provides an overview of some key concepts in multilevel
modeling.

>>>>

\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{ulem}

@@

Understanding and effectively handling missing data within multilevel
structures are crucial for preserving the integrity of analyses and
deriving accurate inferences.

Many datasets include individuals that are clustered together, for
example by geographic region. In the simplest case, each individual is a
unit (e.g., a student) which is nested within a single cluster (e.g., a
school class). More complex clustered structures may occur when there
are multiple hierarchical levels (e.g., patients within hospitals within
regions across countries), or when the clustering is non-nested (e.g.,
electronic health record data from diverse settings and populations
within large databases). The hierarchical structures of such clustered
data may be captured using multilevel analysis techniques.

With clustered data we generally assume that individuals from the same
cluster tend to be more similar than individuals from other clusters. In
statistical terms, this implies that observations from the same cluster
are not independent and may in fact be correlated. If this correlation
is left unaddressed, estimates of \emph{p} values, confidence intervals
even model parameters are prone to bias \citep{loca01}. Statistical
methods for clustered data typically adopt hierarchical models that
explicitly describe the grouping of observations. These models are also
known as `multilevel models', `hierarchical models', `mixed effect
models', `random effect models', and in the context of time-to-event
data as `frailty models'. Table \ref{tab:clus} provides an overview of
some key concepts in multilevel modeling.

In the context of multilevel data, missingness can occur at different
levels, complicating the interpretation and reliability of results.
